### 2024-07-02 Paper/appendix.tex
Updates from Overleaf

        \vspace{0.5cm}
        \Large
        Christian Vedel, University of Southern Denmark,\\
        \small
        christian-vs@sam.sdu.dk; 
        \url{https://github.com/christianvedels/A_perfect_storm}

@@

\begin{equation}
\label{eq:MA2}
{MA}_p = \sum_{h \in H} [CostDist(p, h; \alpha) + 1]^\theta
\end{equation}

@@

\begin{table}
\centering
\caption{\label{tab:reg_trade} Channel introduction and trade}
\begin{tabular}{lccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{traffic}     & log(traffic+1)  & arcsinh(traffic)  & $1[traffic>0]$\\
                        & (1)            & (2)            & (3)             & (4)             & (5)\\  
                        & Poisson        & Poisson        & OLS             & OLS             & OLS\\  
   \midrule
   Post$\times$east     & -0.4896$^{**}$ & -0.4817$^{*}$  & -0.0029         & 0.0115          & 0.0115\\   
                        & (0.2172)       & (0.2489)       & (0.0915)        & (0.1741)        & (0.1741)\\   
   Post$\times$middle   & 5.557$^{***}$  & 11.76$^{***}$  & 0.9672$^{***}$  & 0.3811$^{***}$  & 0.3811$^{***}$\\   
                        & (0.2151)       & (0.2471)       & (0.0584)        & (0.0233)        & (0.0233)\\   
   Post$\times$west     & 4.129$^{***}$  & 4.698$^{***}$  & 0.3821          & 0.3194$^{**}$   & 0.3194$^{**}$\\   
                        & (0.5090)       & (0.4714)       & (0.2635)        & (0.1263)        & (0.1263)\\   
   \midrule
   Observations         & 13,356         & 11,214         & 13,356          & 13,356          & 13,356\\  
   \midrule
   1807-1814 excl.      & No             & Yes            & No              & No              & No\\
   1825-1833 excl.      & No             & Yes            & No              & No              & No\\
   \midrule \midrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\textit{Notes:} Cluster-robust standard errors in the parenthesis. Clustered at the port level. Coloumn (1) shows Poisson results. Column (2) shows Poisson results but where the years of the Napoleonic wars are removed. Column (3) and (4) show OLS results using the $log(x+1)$ or $archsinh(x)$ transformation to deal with zero outcomes. Column (5) shows extensive margin results. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. \\ \textit{Source: Danish census data}}
}
\end{table}

@@

\subsection{Multiverse of the effect in different comparison groups and parameter choices, 1901} 
\FloatBarrier
\begin{table}[H]
\centering
\caption{\label{tab:pop1} Regression results for population size}
\footnotesize
\begin{tabular}{lcc}
   \tabularnewline \midrule \midrule
   Outcome: & \multicolumn{2}{c}{log(Population)}\\
                                                    & (1)             & (2)\\  
                                                    & Dummy approach  & Market access approach\\  
   \midrule
   Year 1787 $\times$ Affected                       & 0.0160          & 0.0379\\   
                                                     & (0.0106)        & (0.0626)\\   
   Year 1834 $\times$ Affected                       & 0.0177          & -0.0146\\   
                                                     & (0.0127)        & (0.0748)\\   
   Year 1840 $\times$ Affected                       & -0.0060         & -0.2651$^{***}$\\   
                                                     & (0.0132)        & (0.0759)\\   
   Year 1845 $\times$ Affected                       & -0.0029         & -0.2531$^{***}$\\   
                                                     & (0.0143)        & (0.0775)\\   
   Year 1850 $\times$ Affected                       & 0.0021          & -0.2466$^{***}$\\   
                                                     & (0.0152)        & (0.0900)\\   
   Year 1860 $\times$ Affected                       & 0.0319$^{*}$    & 0.0183\\   
                                                     & (0.0175)        & (0.0972)\\   
   Year 1880 $\times$ Affected                       & 0.1379$^{***}$  & 0.8349$^{***}$\\   
                                                     & (0.0203)        & (0.1155)\\   
   Year 1901 $\times$ Affected                       & 0.2364$^{***}$  & 1.591$^{***}$\\   
                                                     & (0.0264)        & (0.1607)\\  
   \midrule
   Observations                                     & 14,301          & 14,301\\
   Parishes                                         & 1,589           & 1,589\\
   \midrule 
   Parish FE                                        & Yes             & Yes\\  
   Year FE                                          & Yes             & Yes\\
   \midrule \midrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\textit{Notes:} Cluster-robust standard errors in the parenthesis. Clustered at the parish level. Affected is either a dummy for being in the West Limfjord or improvement in market access, which is indicated by the headers of the results. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. \\ \textit{Source: Danish census data}}
}
\end{table}

@@

\begin{figure}[H]
    \centering
    \caption{Multiverse of the effect in different comparison groups and parameter choices, 1787}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult1} Multiverse of control groups\\Dummy approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_dummy.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult2} Multiverse of control groups\\Market access approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA.png}
    \end{subfigure}
    \vspace{0.45cm}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult3} Multiverse of feasible parameters\\Market access approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_param.png}
    \end{subfigure}
    \parbox{0.9\textwidth}{
    \caption*{\footnotesize \textit{Notes:} This is the multiverse of parameter estimates of the effect in 1901 given different feasible choices that could have been made for how to run the analysis. In panel a and panel b, 'A', 'B', and 'C', represents subgroups of the data. 'A' is the result, when the regression is computed using only parishes with a centroid less than 5 km from the coast. 'B' is the subgroups, where all parishes in around Copenhagen are excluded, 'C' is the subgroup of parishes, where the control group does not contain any parishes within 100 km of the Limfjord. 'D' represents the result when using only parishes located within 5 km of a market town. Panel (c) represents the effect given different market access parameters. For enhanced comparability, the log change in market access is standardized to unit variance and zero mean. \\ \textit{Source: Danish census data}}
} \label{fig:pop2}
\end{figure}

\begin{figure}[H]
    \centering
    \caption{Multiverse of the effect in different comparison groups and parameter choices}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult1} Multiverse of control groups\\Dummy approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_dummy_1787.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult2} Multiverse of control groups\\Market access approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_1787.png}
    \end{subfigure}
    \vspace{0.45cm}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{\label{fig:mult3} Multiverse of feasible parameters\\Market access approach}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_param_1787.png}
    \end{subfigure}
    \caption*{Notes: Multiverse results for 1787. If any of these were different from zero it would indicate the existence of pretends. The dotted line indicate the default parameter estimate. The solid line is at zero.}
    \label{fig:pop2}
\end{figure}

@@

\begin{table}[H]
\centering
\caption{\label{tab:cs_estimates} Callaway and Sant'Anna estimates}
\footnotesize
\begin{tabular}{lccc}
   \tabularnewline \midrule \midrule
   Outcome: & \multicolumn{3}{c}{log(Population)}\\
            & (1)           & (2)             & (3)\\  
   \midrule
    1801 & -0.0152      & -0.0273     & -0.0273 \\
         & (0.0114)     & (0.0141)    & (0.0133) \\
    1834 & 0.0221       & 0.0041      & 0.0041 \\
         & (0.0133)     & (0.0148)    & (0.0145) \\
    1840 & 0.0004       & -0.0097     & -0.0097 \\
         & (0.0132)     & (0.0154)    & (0.0145) \\
    1845 & 0.0031       & -0.0058     & -0.0058 \\
         & (0.0137)     & (0.0156)    & (0.0149) \\
    1850 & 0.0076       & -0.0040     & -0.0040 \\
         & (0.0146)     & (0.0174)    & (0.0160) \\
    1860 & 0.0343       & 0.0087      & 0.0087 \\
         & (0.0166)     & (0.0187)    & (0.0194) \\
    1880 & 0.1336*      & 0.0873*     & 0.0873* \\
         & (0.0198)     & (0.0229)    & (0.0233) \\
    1901 & 0.2262*      & 0.1590*     & 0.1590* \\
         & (0.0263)     & (0.0276)    & (0.0310)\\  
   \midrule
   Observations & 14,2741 & 14,274 & 14,274\\
   \midrule \midrule
   \multicolumn{4}{l}{\emph{'*' confidence band (95 percent) does not cover 0}}\\
\end{tabular}
\parbox{0.6\textwidth}{
\caption*{Notes: Effect using the estimator proposed by Callaway \& Sant’Anna (2021). Column (1) includes no covariates. Column (2) adjusts for pre-event covariates. Column (3) adjusts for pre-event covariates including pre-event population. \\ \textit{Source: Danish census data}}
}

@@

\FloatBarrier
\subsection{All occupational major categories estimates} 
\begin{table}[]
    \centering
    \caption{\label{tab:occ1} Effect on occupation in 1901 (HISCO first digit 1 to 3)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
0/1 & MA & 3: log(x+1) & -0.642 (0.337) & 1589\\
0/1 & MA & 4: asinh(x) & -0.595 (0.397) & 1589\\
0/1 & MA & 1: Extensive & 0.414 (0.139) & 1589\\
0/1 & MA & 2: Intensive & -0.41 (0.445) & 1342\\
0/1 & Dummy & 3: log(x+1) & -0.083 (0.06) & 1589\\
0/1 & Dummy & 4: asinh(x) & -0.081 (0.07) & 1589\\
0/1 & Dummy & 1: Extensive & 0.064 (0.025) & 1589\\
0/1 & Dummy & 2: Intensive & -0.047 (0.079) & 1342\\
2 & MA & 3: log(x+1) & -0.871 (0.463) & 1589\\
2 & MA & 4: asinh(x) & -0.561 (0.521) & 1589\\
2 & MA & 1: Extensive & 0.182 (0.148) & 1589\\
2 & Dummy & 3: log(x+1) & -0.085 (0.085) & 1589\\
2 & Dummy & 2: Intensive & 0.081 (0.148) & 764\\
2 & Dummy & 4: asinh(x) & -0.056 (0.096) & 1589\\
2 & MA & 2: Intensive & 0.04 (0.761) & 764\\
2 & Dummy & 1: Extensive & -0.015 (0.025) & 1589\\
3 & MA & 2: Intensive & 1.962 (4.096) & 75\\
3 & Dummy & 2: Intensive & 1.252 (0.472) & 75\\
3 & MA & 1: Extensive & 1.128*** (0.259) & 1589\\
3 & MA & 4: asinh(x) & 0.697 (0.479) & 1589\\
3 & MA & 3: log(x+1) & 0.486 (0.381) & 1589\\
3 & Dummy & 1: Extensive & 0.169*** (0.044) & 1589\\
3 & Dummy & 4: asinh(x) & 0.101 (0.087) & 1589\\
3 & Dummy & 3: log(x+1) & 0.073 (0.07) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 0/1, 2 or 3 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

\begin{table}[]
    \centering
    \caption{\label{tab:occ2} Effect on occupation in 1901 (HISCO first digit 4 to 9)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
4 & MA & 2: Intensive & -4.772 (3.826) & 28\\
4 & MA & 4: asinh(x) & -1.342 (0.576) & 1589\\
4 & MA & 3: log(x+1) & -1.121 (0.489) & 1589\\
4 & Dummy & 2: Intensive & -0.353 (0.402) & 28\\
4 & Dummy & 4: asinh(x) & -0.182 (0.103) & 1589\\
4 & Dummy & 3: log(x+1) & -0.143 (0.087) & 1589\\
4 & MA & 1: Extensive & -0.123 (0.202) & 1589\\
4 & Dummy & 1: Extensive & -0.058 (0.036) & 1589\\
5 & MA & 4: asinh(x) & -0.943 (0.554) & 1589\\
5 & MA & 1: Extensive & -0.662*** (0.163) & 1589\\
5 & MA & 3: log(x+1) & -0.625 (0.462) & 1589\\
5 & Dummy & 2: Intensive & 0.309 (0.159) & 660\\
5 & MA & 2: Intensive & 0.302 (0.881) & 660\\
5 & Dummy & 3: log(x+1) & 0.057 (0.079) & 1589\\
5 & Dummy & 4: asinh(x) & 0.042 (0.094) & 1589\\
5 & Dummy & 1: Extensive & -0.031 (0.028) & 1589\\
6 & MA & 2: Intensive & 1.173*** (0.196) & 1545\\
6 & MA & 1: Extensive & -0.243*** (0.049) & 1589\\
6 & Dummy & 2: Intensive & 0.197*** (0.031) & 1545\\
6 & MA & 4: asinh(x) & -0.123 (0.322) & 1589\\
6 & Dummy & 3: log(x+1) & 0.085 (0.036) & 1589\\
6 & Dummy & 4: asinh(x) & 0.072 (0.038) & 1589\\
6 & MA & 3: log(x+1) & 0.025 (0.294) & 1589\\
6 & Dummy & 1: Extensive & -0.024*** (0.004) & 1589\\
7/8/9 & MA & 2: Intensive & 1.763*** (0.339) & 1530\\
7/8/9 & MA & 4: asinh(x) & 0.813 (0.39) & 1589\\
7/8/9 & MA & 3: log(x+1) & 0.709 (0.358) & 1589\\
7/8/9 & MA & 1: Extensive & -0.218*** (0.05) & 1589\\
7/8/9 & Dummy & 2: Intensive & 0.215** (0.063) & 1530\\
7/8/9 & Dummy & 4: asinh(x) & 0.123 (0.068) & 1589\\
7/8/9 & Dummy & 3: log(x+1) & 0.11 (0.063) & 1589\\
7/8/9 & Dummy & 1: Extensive & -0.02 (0.007) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 4, 5, or 6/8/9 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

@@

```{pseudo code}
B = 1000 # Number of Monte Carlo samples

@@

# Converting to P({coins}|t)
P_of_coins_given_t = c_hat * P_of_t_given_coins
```

@@

\caption{\label{tab:A_arch1} All parameters of table 3 columns 1-4}

@@

                                                    & (0.0091)        & (0.0009)        & (0.0103)              & (0.0019)\\   

@@

                                                    & (0.0047)        & (0.0005)        & (0.0068)              & (0.0013)\\   

@@

                                                    & (0.0048)        & (0.0005)        & (0.0067)              & (0.0013)\\   

@@

                                                    & (0.0034)        & (0.0004)        & (0.0041)              & (0.0008)\\   

@@

                                                    & (0.0037)        & (0.0004)        & (0.0019)              & (0.0004)\\   

@@

                                                    & (0.0026)        & (0.0003)        & (0.0032)              & (0.0006)\\   

@@

                                                    & (0.0121)        & (0.0012)        & (0.0163)              & (0.0033)\\   

@@

                                                    & (0.0122)        & (0.0012)        & (0.0168)              & (0.0034)\\   
   Year1200 $\times$ Affected                       & -0.0327$^{**}$  & -0.0049$^{***}$ & -0.0736$^{***}$       & -0.0069$^{*}$\\   
                                                    & (0.0150)        & (0.0013)        & (0.0171)              & (0.0035)\\   

@@

                                                    & (0.0194)        & (0.0017)        & (0.0190)              & (0.0038)\\   

@@

                                                    & (0.0223)        & (0.0030)        & (0.0179)              & (0.0032)\\   

@@

                                                    & (0.0267)        & (0.0036)        & (0.0192)              & (0.0032)\\   

>>>>

        \vspace{0.5cm}
        \large
        Christian Vedel, University of Southern Denmark,\\
        \small
        \vspace{0.25cm}
        christian-vs@sam.sdu.dk; 
        \url{https://github.com/christianvedels/A_perfect_storm}

@@

\begin{equation}
\label{eq:MA2_a}
{MA}_p = \sum_{h \in H} [CostDist(p, h; \alpha) + 1]^\theta
\end{equation}

@@

\begin{table}
\centering
\caption{Channel introduction and trade} \label{tab:reg_trade}
\begin{tabular}{lccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{traffic}     & log(traffic+1)  & arcsinh(traffic)  & $1[traffic>0]$\\
                        & (1)            & (2)            & (3)             & (4)             & (5)\\  
                        & Poisson        & Poisson        & OLS             & OLS             & OLS\\  
   \midrule
   Post$\times$east     & -0.4896$^{**}$ & -0.4817$^{*}$  & -0.0029         & 0.0115          & 0.0115\\   
                        & (0.2172)       & (0.2489)       & (0.0915)        & (0.1741)        & (0.1741)\\   
   Post$\times$middle   & 5.557$^{***}$  & 11.76$^{***}$  & 0.9672$^{***}$  & 0.3811$^{***}$  & 0.3811$^{***}$\\   
                        & (0.2151)       & (0.2471)       & (0.0584)        & (0.0233)        & (0.0233)\\   
   Post$\times$west     & 4.129$^{***}$  & 4.698$^{***}$  & 0.3821          & 0.3194$^{**}$   & 0.3194$^{**}$\\   
                        & (0.5090)       & (0.4714)       & (0.2635)        & (0.1263)        & (0.1263)\\   
   \midrule
   Observations         & 13,356         & 11,214         & 13,356          & 13,356          & 13,356\\  
   \midrule
   1807-1814 excl.      & No             & Yes            & No              & No              & No\\
   1825-1833 excl.      & No             & Yes            & No              & No              & No\\
   \midrule \midrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\textit{Notes:} Cluster-robust standard errors in the parenthesis. Clustered at the port level. Coloumn (1) shows Poisson results. Column (2) shows Poisson results but where the years of the Napoleonic wars are removed. Column (3) and (4) show OLS results using the $log(x+1)$ or $archsinh(x)$ transformation to deal with zero outcomes. Column (5) shows extensive margin results. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. \\ \textit{Source: Danish census data}}
}
\end{table}

@@

\subsection{Multiverse of the effect in different comparison groups and parameter choices, 1901} 
\FloatBarrier
\begin{table}[H]
\centering
\caption{Regression results for population size} \label{tab:pop1}
\footnotesize
\begin{tabular}{lcc}
   \tabularnewline \midrule \midrule
   Outcome: & \multicolumn{2}{c}{log(Population)}\\
                                                    & (1)             & (2)\\  
                                                    & Dummy approach  & Market access approach\\  
   \midrule
   Year 1787 $\times$ Affected                       & 0.0160          & 0.0379\\   
                                                     & (0.0106)        & (0.0626)\\   
   Year 1834 $\times$ Affected                       & 0.0177          & -0.0146\\   
                                                     & (0.0127)        & (0.0748)\\   
   Year 1840 $\times$ Affected                       & -0.0060         & -0.2651$^{***}$\\   
                                                     & (0.0132)        & (0.0759)\\   
   Year 1845 $\times$ Affected                       & -0.0029         & -0.2531$^{***}$\\   
                                                     & (0.0143)        & (0.0775)\\   
   Year 1850 $\times$ Affected                       & 0.0021          & -0.2466$^{***}$\\   
                                                     & (0.0152)        & (0.0900)\\   
   Year 1860 $\times$ Affected                       & 0.0319$^{*}$    & 0.0183\\   
                                                     & (0.0175)        & (0.0972)\\   
   Year 1880 $\times$ Affected                       & 0.1379$^{***}$  & 0.8349$^{***}$\\   
                                                     & (0.0203)        & (0.1155)\\   
   Year 1901 $\times$ Affected                       & 0.2364$^{***}$  & 1.591$^{***}$\\   
                                                     & (0.0264)        & (0.1607)\\  
   \midrule
   Observations                                     & 14,301          & 14,301\\
   Parishes                                         & 1,589           & 1,589\\
   \midrule 
   Parish FE                                        & Yes             & Yes\\  
   Year FE                                          & Yes             & Yes\\
   \midrule \midrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\textit{Notes:} Cluster-robust standard errors in the parenthesis. Clustered at the parish level. Affected is either a dummy for being in the West Limfjord or improvement in market access, which is indicated by the headers of the results. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. \\ \textit{Source: Danish census data}}
}
\end{table}

@@

\begin{figure}[H]
    \centering
    \caption{Multiverse of the effect in different comparison groups and parameter choices, 1787}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of control groups\\Dummy approach} \label{fig:mult1_1787}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_dummy.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of control groups\\Market access approach} \label{fig:mult2_1787}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA.png}
    \end{subfigure}
    \vspace{0.45cm}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of feasible parameters\\Market access approach} \label{fig:mult3_1787}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_param.png}
    \end{subfigure}
    \parbox{0.9\textwidth}{
    \caption*{\footnotesize \textit{Notes:} This is the multiverse of parameter estimates of the effect in 1901 given different feasible choices that could have been made for how to run the analysis. In panel a and panel b, 'A', 'B', and 'C', represents subgroups of the data. 'A' is the result, when the regression is computed using only parishes with a centroid less than 5 km from the coast. 'B' is the subgroups, where all parishes in around Copenhagen are excluded, 'C' is the subgroup of parishes, where the control group does not contain any parishes within 100 km of the Limfjord. 'D' represents the result when using only parishes located within 5 km of a market town. Panel (c) represents the effect given different market access parameters. For enhanced comparability, the log change in market access is standardized to unit variance and zero mean. \\ \textit{Source: Danish census data}}
} \label{fig:pop2_1787}
\end{figure}

\begin{figure}[H]
    \centering
    \caption{Multiverse of the effect in different comparison groups and parameter choices}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of control groups\\Dummy approach} \label{fig:mult1}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_dummy_1787.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of control groups\\Market access approach} \label{fig:mult2}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_1787.png}
    \end{subfigure}
    \vspace{0.45cm}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \caption{Multiverse of feasible parameters\\Market access approach} \label{fig:mult3}
        \includegraphics[width=\textwidth]{Plots/Regression_plots/Multiverse_MA_param_1787.png}
    \end{subfigure}
    \caption*{Notes: Multiverse results for 1787. If any of these were different from zero it would indicate the existence of pretends. The dotted line indicate the default parameter estimate. The solid line is at zero.}
    \label{fig:pop2}
\end{figure}

@@

\begin{table}[H]
\centering
\caption{Callaway and Sant'Anna estimates} \label{tab:cs_estimates}
\footnotesize
\begin{tabular}{lccc}
   \tabularnewline \midrule \midrule
   Outcome: & \multicolumn{3}{c}{log(Population)}\\
            & (1)           & (2)             & (3)\\  
   \midrule
    1801 & -0.0152      & -0.0273     & -0.0273 \\
         & (0.0114)     & (0.0141)    & (0.0133) \\
    1834 & 0.0221       & 0.0041      & 0.0041 \\
         & (0.0133)     & (0.0148)    & (0.0145) \\
    1840 & 0.0004       & -0.0097     & -0.0097 \\
         & (0.0132)     & (0.0154)    & (0.0145) \\
    1845 & 0.0031       & -0.0058     & -0.0058 \\
         & (0.0137)     & (0.0156)    & (0.0149) \\
    1850 & 0.0076       & -0.0040     & -0.0040 \\
         & (0.0146)     & (0.0174)    & (0.0160) \\
    1860 & 0.0343       & 0.0087      & 0.0087 \\
         & (0.0166)     & (0.0187)    & (0.0194) \\
    1880 & 0.1336*      & 0.0873*     & 0.0873* \\
         & (0.0198)     & (0.0229)    & (0.0233) \\
    1901 & 0.2262*      & 0.1590*     & 0.1590* \\
         & (0.0263)     & (0.0276)    & (0.0310)\\  
   \midrule
   Observations & 14,2741 & 14,274 & 14,274\\
   \midrule \midrule
   \multicolumn{4}{l}{\emph{'*' confidence band (95 percent) does not cover 0}}\\
\end{tabular}
\parbox{0.6\textwidth}{
\caption*{Notes: Effect using the estimator proposed by Callaway \& Sant’Anna (2021). Column (1) includes no covariates. Column (2) adjusts for pre-event covariates. Column (3) adjusts for pre-event covariates including pre-event population. \\ \textit{Source: Danish census data}}
}

@@

\FloatBarrier
\subsection{All occupational major categories estimates}

\begin{table}
    \centering
    \caption{Effect on occupation in 1901 (HISCO first digit 1 to 3)} \label{tab:occ1}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
0/1 & MA & 3: log(x+1) & -0.642 (0.337) & 1589\\
0/1 & MA & 4: asinh(x) & -0.595 (0.397) & 1589\\
0/1 & MA & 1: Extensive & 0.414 (0.139) & 1589\\
0/1 & MA & 2: Intensive & -0.41 (0.445) & 1342\\
0/1 & Dummy & 3: log(x+1) & -0.083 (0.06) & 1589\\
0/1 & Dummy & 4: asinh(x) & -0.081 (0.07) & 1589\\
0/1 & Dummy & 1: Extensive & 0.064 (0.025) & 1589\\
0/1 & Dummy & 2: Intensive & -0.047 (0.079) & 1342\\
2 & MA & 3: log(x+1) & -0.871 (0.463) & 1589\\
2 & MA & 4: asinh(x) & -0.561 (0.521) & 1589\\
2 & MA & 1: Extensive & 0.182 (0.148) & 1589\\
2 & Dummy & 3: log(x+1) & -0.085 (0.085) & 1589\\
2 & Dummy & 2: Intensive & 0.081 (0.148) & 764\\
2 & Dummy & 4: asinh(x) & -0.056 (0.096) & 1589\\
2 & MA & 2: Intensive & 0.04 (0.761) & 764\\
2 & Dummy & 1: Extensive & -0.015 (0.025) & 1589\\
3 & MA & 2: Intensive & 1.962 (4.096) & 75\\
3 & Dummy & 2: Intensive & 1.252 (0.472) & 75\\
3 & MA & 1: Extensive & 1.128*** (0.259) & 1589\\
3 & MA & 4: asinh(x) & 0.697 (0.479) & 1589\\
3 & MA & 3: log(x+1) & 0.486 (0.381) & 1589\\
3 & Dummy & 1: Extensive & 0.169*** (0.044) & 1589\\
3 & Dummy & 4: asinh(x) & 0.101 (0.087) & 1589\\
3 & Dummy & 3: log(x+1) & 0.073 (0.07) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 0/1, 2 or 3 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

\begin{table}
    \centering
    \caption{Effect on occupation in 1901 (HISCO first digit 4 to 9)} \label{tab:occ2}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
4 & MA & 2: Intensive & -4.772 (3.826) & 28\\
4 & MA & 4: asinh(x) & -1.342 (0.576) & 1589\\
4 & MA & 3: log(x+1) & -1.121 (0.489) & 1589\\
4 & Dummy & 2: Intensive & -0.353 (0.402) & 28\\
4 & Dummy & 4: asinh(x) & -0.182 (0.103) & 1589\\
4 & Dummy & 3: log(x+1) & -0.143 (0.087) & 1589\\
4 & MA & 1: Extensive & -0.123 (0.202) & 1589\\
4 & Dummy & 1: Extensive & -0.058 (0.036) & 1589\\
5 & MA & 4: asinh(x) & -0.943 (0.554) & 1589\\
5 & MA & 1: Extensive & -0.662*** (0.163) & 1589\\
5 & MA & 3: log(x+1) & -0.625 (0.462) & 1589\\
5 & Dummy & 2: Intensive & 0.309 (0.159) & 660\\
5 & MA & 2: Intensive & 0.302 (0.881) & 660\\
5 & Dummy & 3: log(x+1) & 0.057 (0.079) & 1589\\
5 & Dummy & 4: asinh(x) & 0.042 (0.094) & 1589\\
5 & Dummy & 1: Extensive & -0.031 (0.028) & 1589\\
6 & MA & 2: Intensive & 1.173*** (0.196) & 1545\\
6 & MA & 1: Extensive & -0.243*** (0.049) & 1589\\
6 & Dummy & 2: Intensive & 0.197*** (0.031) & 1545\\
6 & MA & 4: asinh(x) & -0.123 (0.322) & 1589\\
6 & Dummy & 3: log(x+1) & 0.085 (0.036) & 1589\\
6 & Dummy & 4: asinh(x) & 0.072 (0.038) & 1589\\
6 & MA & 3: log(x+1) & 0.025 (0.294) & 1589\\
6 & Dummy & 1: Extensive & -0.024*** (0.004) & 1589\\
7/8/9 & MA & 2: Intensive & 1.763*** (0.339) & 1530\\
7/8/9 & MA & 4: asinh(x) & 0.813 (0.39) & 1589\\
7/8/9 & MA & 3: log(x+1) & 0.709 (0.358) & 1589\\
7/8/9 & MA & 1: Extensive & -0.218*** (0.05) & 1589\\
7/8/9 & Dummy & 2: Intensive & 0.215** (0.063) & 1530\\
7/8/9 & Dummy & 4: asinh(x) & 0.123 (0.068) & 1589\\
7/8/9 & Dummy & 3: log(x+1) & 0.11 (0.063) & 1589\\
7/8/9 & Dummy & 1: Extensive & -0.02 (0.007) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 4, 5, or 6/8/9 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

@@

\begin{verbatim}
    ```{pseudo code}
    B = 1000 # Number of Monte Carlo samples

@@

    # Converting to P({coins}|t)
    P_of_coins_given_t = c_hat * P_of_t_given_coins
    ```
\end{verbatim}

@@

\caption{All parameters of table 3 columns 1-4} \label{tab:A_arch1}

@@

                                                    & (0.0092)        & (0.0009)        & (0.0101)              & (0.0018)\\   

@@

                                                    & (0.0049)        & (0.0005)        & (0.0068)              & (0.0013)\\   

@@

                                                    & (0.0051)        & (0.0006)        & (0.0068)              & (0.0013)\\   

@@

                                                    & (0.0035)        & (0.0004)        & (0.0041)              & (0.0008)\\   

@@

                                                    & (0.0038)        & (0.0004)        & (0.0018)              & (0.0003)\\   

@@

                                                    & (0.0025)        & (0.0003)        & (0.0032)              & (0.0006)\\   

@@

                                                    & (0.0121)        & (0.0011)        & (0.0165)              & (0.0032)\\   

@@

                                                    & (0.0121)        & (0.0011)        & (0.0170)              & (0.0033)\\   
   Year1200 $\times$ Affected                       & -0.0327$^{**}$  & -0.0049$^{***}$ & -0.0736$^{***}$       & -0.0069$^{**}$\\   
                                                    & (0.0151)        & (0.0013)        & (0.0174)              & (0.0034)\\   

@@

                                                    & (0.0199)        & (0.0018)        & (0.0193)              & (0.0038)\\   

@@

                                                    & (0.0236)        & (0.0032)        & (0.0178)              & (0.0031)\\   

@@

                                                    & (0.0273)        & (0.0037)        & (0.0185)              & (0.0031)\\   
